16s lefse

### 2021-04-14 scripts/56_rethinking_genera.Rmd
update

# do not standardize the log transformed relative abundance 
meta <- read_csv('../data/amplicon/stool/combined_2_meta_expanded.csv')  %>% 
  full_join(genera)

>>>>

# do not standardize the log transformed relative abundance 
meta <- read_csv('../data/amplicon/stool/combined_2_meta_expanded.csv')  %>% 
  inner_join(genera)

### 2021-04-14 scripts/57_16s_lefse.Rmd
update

```{r}
dat <- genera %>% 
  filter(genus == 'Ruminococcus') %>% 
  gather('sampleid', 'relab', names(.)[2]:names(.)[ncol(.)]) %>% 
  full_join(meta) %>% 
  mutate(logrelab =  log10(relab + 2e-6))

yes <- dat %>% 
  filter(cr_d100 == 'yes')
no <- dat %>% 
  filter(cr_d100 == 'no')

dat %>% 
  #filter(center == 'M') %>% 
  mutate(logrelab =  log10(relab + 2e-6)) %>% 
  ggboxplot(x = 'cr_d100', y = 'logrelab', add = 'jitter') +
stat_compare_means(comparisons= list(c('yes', 'no')),
										label= "p.signif",
										method= 'wilcox.test',
										correct=FALSE)

t.test(yes$logrelab, no$logrelab)

>>>>

```{r}
# dat <- genera %>% 
#   filter(genus == 'Ruminococcus') %>% 
#   gather('sampleid', 'relab', names(.)[2]:names(.)[ncol(.)]) %>% 
#   full_join(meta) %>% 
#   mutate(logrelab =  log10(relab + 2e-6)) 
# 
# yes <- dat %>% 
#   filter(cr_d100 == 'yes')
# no <- dat %>% 
#   filter(cr_d100 == 'no')
# 
# 
# dat %>% 
#   #filter(center == 'M') %>% 
#   mutate(logrelab =  log10(relab + 2e-6)) %>% 
#   ggboxplot(x = 'cr_d100', y = 'logrelab', add = 'jitter') +
# stat_compare_means(comparisons= list(c('yes', 'no')),
# 										label= "p.signif",
# 										method= 'wilcox.test',
# 										correct=FALSE)
# 
# t.test(yes$logrelab, no$logrelab)
